Reduced plasticity and variance in physiological rates for ectotherm populations under climate change

### 2024-02-10 ms.qmd
Added funding

## Funding
This work was partially supported by an Australian Research Council (ARC) Discovery Early Career Research Award (DE150101774) and ARC Future Fellowship (FT220100276) to DWAN.

>>>>

## Funding
DWAN is supported by an Australian Research Council (ARC) Future Fellowship (FT220100276) and ARC Discovery Project (DP210101152). SN is supported by ARC Discovery Project Grants (DP210100812 and DP230101248).
